# Getting and Cleaning Data Quiz 2

## Question 1

Register an application with the Github API here [https://github.com/settings/applications].
Access the API to get information on your instructors repositories (hint: this is the url you want "https://api.github.com/users/jtleek/repos"). Use this data to find the time that the datasharing repo was created. What time was it created?

This tutorial may be useful (https://github.com/hadley/httr/blob/master/demo/oauth2-github.r). 

```{r}
library(httr)
myapp <-oauth_app("github",key="474d15e5f84fc6c0cf41",
                  secret = "e5100b0c2ff7774c04c2c6185c27382f05ba9838")
github_token <- oauth2.0_token(oauth_endpoints("github"), myapp)


# Use the API
gtoken <- config(token = github_token)
req <- with_config(gtoken, GET("https://api.github.com/users/jtleek/repos"))
stop_for_status(req)
repo_list <- content(req)
Q1 <- c()
for(i in 1:length(repo_list)){
    repo <- repo_list[[i]]
    if(repo$name == "datasharing"){
        Q1 = repo
        break
    }
}


if (length(Q1) == 0){
    message("Repository Not Found")
} else {
    message("Datasharing was created at ", Q1$created_at)
}
```


## Question 2
The sqldf package allows for execution of SQL commands on R data frames. We will use the sqldf package to practice the queries we might send with the dbSendQuery command in RMySQL.

Download the American Community Survey data and load it into an R object called 
`acs`

```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
if(!file.exists("data")){
    dir.create("data")
}
download.file(fileUrl, destfile = "./data/survey.csv")
acs <- read.table("./data/survey.csv", sep = ",", header = TRUE)

library(sqldf)
library(RMySQL)

sqldf("select pwgtp1 from acs where agep <50")
```

## Question 4
How many characters are in the 10th, 20th, 30th and 100th lines of HTML from this page:

http://biostat.jhsph.edu/~jleek/contact.html

(Hint: the nchar() function in R may be helpful)
```{r}
con <- url("http://biostat.jhsph.edu/~jleek/contact.html") 
htmlcode <- readLines(con)
close(con)
library(XML)
library(RCurl)
q4 <-c()
sapply(c(10,20,30,100),function(x) {q4 <- c(q4, nchar(htmlcode[x]))})

```

## Question 5
Read this data set into R and report the sum of the numbers in the fourth of the nine columns.

https://d396qusza40orc.cloudfront.net/getdata%2Fwksst8110.for
Original source of the data: http://www.cpc.ncep.noaa.gov/data/indices/wksst8110.for

Hint this is a fixed width file format

```{r}
fileUrl5 <- "https://d396qusza40orc.cloudfront.net/getdata%2Fwksst8110.for"
if(!file.exists("data")){
    dir.create("data")
}
download.file(fileUrl5, destfile = "./data/q5.for")
library(readr)
q5data <- read_fwf("./data/q5.for", skip=4,fwf_widths(c(12,7,4,9,4,9,4,9,4)))
summation <- sum(q5data$X4)
summation

```
